### 2016-02-19 paper.tex
Clean up abstract

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. A peak power coefficient $C_P = 0.37$ and
rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
$\lambda_0 = 3.1$. Weak linear $Re$-dependence was achieved at a turbine
diameter Reynolds number $Re_D \approx 10^6$. The effects of blade support strut
drag on turbine performance were investigated by covering the rotor's NACA 0021
struts with cylinders. As expected, this modification drastically reduced the
rotor power coefficient. Strut drag was also measured for the NACA 0021 and
cylindrical configurations with the blades removed. For $\lambda=\lambda_0$,
wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
turbulence kinetic energy, and mean kinetic energy transport were compared with
results from a high solidity turbine acquired with the same test apparatus. Like
the high solidity case, mean vertical advection was calculated to be the largest
contributor to near-wake recovery. However, overall, lower levels of streamwise
wake recovery were calculated for the RM2 case---a consequence of both the
relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. However,

>>>>

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. A peak power coefficient $C_P = 0.37$ and
rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
$\lambda_0 = 3.1$. Weak linear $Re$-dependence of the power coefficient was
achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects
of blade support strut drag on turbine performance were investigated by covering
the rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced the rotor power coefficient. Strut drag losses were also
measured for the NACA 0021 and cylindrical configurations with the blades
removed. For $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$
downstream. Mean velocity, turbulence kinetic energy, and mean kinetic energy
transport were compared with results from a high solidity turbine acquired with
the same test apparatus. Like the high solidity case, mean vertical advection
was calculated to be the largest contributor to near-wake recovery. However,
overall, lower levels of streamwise wake recovery were calculated for the RM2
case---a consequence of both the relatively low solidity and tapered blades
reducing blade tip vortex shedding---responsible for mean vertical
advection---and lower levels of turbulence caused by higher operating tip speed
ratio and therefore reduced dynamic stall.
